\newpage
\numberwithin{equation}{section}
\newcommand{\spq}{S(q,p^o(q))}
\newcommand{\pq}{p^o(q)}
\thispagestyle{empty}
\section{Coordinating the newsvendor with \textit{price-dependent} demand}


\subsection{Model and analysis}
Now the retailer chooses his price in addition to his order quantity. Let $F(q|p)$ be the distribution function of demand, where $p$ is the retail price. Assume $\frac{\partial F(q|p)}{\partial p}>0$. To obtain initial insights, assume the retailer sets his \textbf{price} \textit{at the same time as} his \textbf{stocking decision} and the price is \textbf{fixed} throughout the season.
\begin{note}
    van Mieghem and Dada (1999). A hybrid model. The retailer chooses $q$, then observes a demand signal and then chooses price.
\end{note}

The integrated channel's profit is 
\begin{equation*}
    \Pi(q,p)=(p-v+g)S(q,p)-(c-v)q-g\mu
\end{equation*}
where $S(q,p)$ is expected sales given the stocking quantity $q$ and the price $p$, and similarly, we have
\begin{equation*}
    S(q,p)=q-\int_0^q F(y|p)dy
\end{equation*}
\begin{note}
    The integrated channel profit function need not be concave nor unimodal (Petruzzi \& Dada 1999)
\end{note}
Let $\pq$ be the supply chain optimal price for a given $q$. The necessary condition for coordination is
\begin{equation}\label{eq:3.1}
    \frac{\partial\Pi(q,p^o(q))}{\partial p}=S(q,p^o(q))+(p^o(q)-v+g)\frac{\partial S(q,p^o(q))}{\partial p}=0.
\end{equation}
\begin{note}
    Either not satisfy the first-order condition or fail to coordinate the quantity decision.
\end{note}

Consider the \textbf{quantity-flexibility} contract. The retailer's profit function is 
\begin{align*}
    \pi_r(q,p,w_q,\delta)=&(p-v+g_r)S(q,p)-(w_q+c_r-v)q\\
    +&(w_q+c_r-v)\int_{(1-\delta)q}^q F(y|p)dy-\mu g_r
\end{align*}
For price coordination the first-order condition must hold,

\begin{align}
\frac{\partial \pi_{\mathrm{r}}\left(q, p^{\mathrm{o}}(q), w_{q}, \delta\right)}{\partial p}=& S\left(q, p^{\mathrm{o}}(q)\right)+\left(p^{\mathrm{o}}(q)-v+g_{\mathrm{r}}\right) \frac{\partial S\left(q, p^{\mathrm{o}}(q)\right)}{\partial p} \nonumber\\
&+\left(w_{q}+c_{\mathrm{r}}-v\right) \int_{(1-\delta) q}^{q} \frac{\partial F\left(y \mid p^{\mathrm{o}}(q)\right)}{\partial p} \mathrm{~d} y \nonumber\\
=& 0\label{eq:3.2}
\end{align}
The second term in \autoref{eq:3.2} is no smaller than the second term in \autoref{eq:3.1}\footnote{The assumption of $\partial F(q|p)/\partial p>0.$}, so the above holds only if the third term is nonpositive. 
But the third term is nonnegative as $w_q+c_r-v\geq 0$, so with a coordinating $w_q$, the coordination of price can only occur if $g_s=0$ and either $w_q=v-c_r$ or $\delta=0$. \textbf{Neither} is desirable. With $w_q=v-c_r$, then supplier has $w_q<c_s$\footnote{Why? An assumption?} which is not acceptable. With $\delta=0$ the contract degenerates to just a wholesale-price contract, so the retailer's quantity action is not optimal. Hence, the quantity-flexibility contract does not coordinate the newsvendor with price-dependent demand.

The \textbf{sales-rebate} contract does not fare better:
\begin{align*}
    \frac{\partial\pi_r(q,\pq,w_s,r,t)}{\partial p}=&\spq+(\pq-v+g_r)\frac{\partial\spq}{\partial p}\\
    &-r\int_t^q\frac{\partial F(y|\pq)}{\partial p}dy
\end{align*}
Since the last term is negative when $r>0$ and $t<q$, we know that the retailer prices below the optimal price\footnote{The above derivative is negative. Why it means that the retailer prices below the optimal price?}. Coordination might be achieved if there is something to induce the retailer to a higher price.

Now consider a \textbf{buyback} contract. The retailer's profit function is 
\begin{equation*}
    \pi_r(q,p,w_b,b)=(p-v+g_r-b)S(q,p)-(w_b-b+c_r-v)q-g_r\mu.
\end{equation*}
For coordination we must have the first-order condition:
\begin{equation}\label{eq:3.3}
    \frac{\partial\pi_r(q,\pq,w_b,r,t)}{\partial p}=\spq+(\pq-v+g_r-b)\frac{\partial\spq}{\partial p}=0.
\end{equation}
But comparing with \autoref{eq:3.1} it holds only if $b=-g_s< 0$ which violates that $b\geq 0$\footnote{If $g_s=0$, then $w_b=c_s$ and $b_s=0$ which means that the supplier earns no positive profit.\label{ft:4}}. Therefore, a buyback contract does not coordinate the newsvendor with price-dependent demand.

The buyback contract fails to coordinate in this setting because the parameters of the coordinating contracts depend on the price: from \autoref{eq:2.5} and \autoref{eq:2.6}, the coordinating parameters are
\begin{align*}
    b&=(1-\lambda)(p-v+g)-g_s\\
    w_b&=\lambda c_s+(1-\lambda)(p+g-c_r)-g_s.
\end{align*}
For a fixed $\lambda$, the coordianting buyback rate and wholesale price are linear in $p$. Hence, the buyback contract coordiantes the newsvendor with price-dependent demand if $b$ and $w_b$ are made \textbf{contingent} on the retail price chosen, or if $b$ and $w_b$ are chosen \textbf{after} the retailer commits to a price (but before the retailer chooses $q$). This is the \textbf{price-discount-sharing} contract\footnote{Bernstein and Federgruen (2000)}, which is called a "bill back" in practice. The retailer gets a lower wholesale price if the retailer reduces his price, i.e., the supplier shares in the cost of a price discount with the retailer. Then we have the retailer profit function:
\begin{align*}
    \pi_r(q,p,w_b,b)&=\lambda(p-v+g)S(q,p)-\lambda(c-v)q-g_r\mu\\
    &=\lambda(\Pi(q,p)+g\mu)-g_r\mu
\end{align*}
Hence, for the retailer as well ass the supplier, $\{q^o,p^o\}$ is optimal for $\lambda\in[0,1]$.

Now consider the \textbf{revenue-sharing} contract. The retailer's profit is 
\begin{equation*}
    \pi_r(q,p,w_r,\phi)=(\phi(p-v)+g_r)S(q,p)-(w_r+c_r-\phi v)q-g_r\mu.
\end{equation*}
Coordination require
\begin{equation}\label{eq:3.4}
    \frac{\pi_r(q,\pq,w_r,\phi)}{\partial p}=\spq+(\pq-v+g_r/\phi)\frac{\partial\spq}{\partial p}=0.
\end{equation}

\begin{itemize}
    \item Consider $g_r=g_s=0$. In this situation,
    \begin{equation*}
        \frac{\partial\pi_r(q,p,w_r,\phi)}{\partial p}=\frac{\partial\Pi(q,p)}{\partial p}
    \end{equation*}
    with \textbf{any} revenue-sharing contract. Thus, the retailer chooses $\pq$ no matter which revenue-sharing contract is chosen. Now revenue sharing is able to coordinate the retailer's quantity decision with precisely the same set of contracts used when the retailer prices is fixed. 

    Recall that with the \textit{fixed price} newsvendor \textbf{revenue sharing} and \textbf{buybacks} are equivalent. Here, the contracts produce different outcomes because with a buyback the retailer's share of revenue $(1-b/p)$ depends on the price, whereas with revenue sharing it is independent of the price, by definition\footnote{The above partial derivative}. However, the \textbf{price contingent buyback} contract (\textbf{price-discount} contract) is equivalent to revenue sharing: if $g_r=g_s=0$, the coordinating revenue-sharing contract yield 
    \begin{equation*}
        \pi_r(q,p,w_r,\phi)=\lambda\Pi(q,p)
    \end{equation*}
    from \autoref{eq:2.10}. And the price contingent buyback contract yield the same profit for any quantity and price from \autoref{eq:2.7},
    \begin{equation*}
        \pi_r(q,p,b(p),w_b(p))=\lambda\Pi(q,p).
    \end{equation*}
    \item Consider at least one of $g_r$ or $g_s$ is larger than $0$. From \autoref{eq:3.4} coordination is achieved only if $\phi=g_r/g$. In this contract both firms \textbf{may} enjoy a positive profit\footnote{Only if $g_r,g_s>0$ then both firms will earn positive profits.}, which contrasts with the single coordination outcome of the buyback contract shown in \autoref{ft:4}. The difficulty with coordination occurs because the coordinating parameters generally depend on the retail price
    \begin{align*}
        \phi&=\lambda+\frac{\lambda g-g_r}{p-v},\\
        w_r&=\lambda(c-v)-c_r+\phi v.
    \end{align*}
    The \textbf{dependence} on the retail price is eliminated only in the special case $\phi=\lambda=g_r/g$.
\end{itemize}

Coordination for all profit allocations is restored even in this case if, like with the buyback contract, the parameters of the revenue-sharing contract are made contingent on the retailer's price. In that case revenue sharing is again equivalent to the price-discount contract: price discounts are contingent buybacks and contingent buybacks are equivalent to contingent revenue sharing.

Consider the final \textbf{quantity discount} contract. The retailer's profit function is 
\begin{equation*}
    \pi_r(q,w_d(q),p)=(p-v+g_r)S(q,p)-(w_d(q)+c_r-v)q-g_r\mu.
\end{equation*}
If $g_s=0$, then 
\begin{equation*}
    \frac{\pi_r(q,w_d(q),p)}{\partial p}=\frac{\partial S(q,p)}{\partial p}+(p-v+g_r)S(q,p)=\frac{\partial \Pi(q,p)}{\partial p}
\end{equation*}
and so $\pq$ is optimal for the retailer. On the otehr hand, if $g_s>0$, then the retailer's pricing decision needs to be distorted for coordination, which the quantity discount does not do.

Assuming $g_s=0$, we still need to check if the quantity is coordinated. Assume that the optimal price is chosen, we have 
\begin{equation*}
    w_d(q)=((1-\lambda)(p^o-v+g)-g_s)\frac{S(q,p^o)}{q}+\lambda(c-v)-c_r+v,
\end{equation*}
where $p^o=\pq$. It follows that 
\begin{align*}
    \pi_r(q,w_d(q),p)=(p-v+g_r)S(q,p)-\lambda(c-v)q-g_r\mu-((1-\lambda)(p^o-v+g)-g_s)S(q,p^o)
\end{align*}
and so $p^o$ is optimal for the retailer\footnote{Notice that $g_s=0$}, 
\begin{equation*}
    \frac{\pi_r(q,w_d(q),p)}{\partial p}=\frac{\partial\Pi(q,p)}{\partial p}.
\end{equation*}
Given $p^o$ is chosen,
\begin{align*}
    \pi_r(q,w_d(q),p^o)&=\lambda(p^o-v+g)S(q,p^o)-\lambda(c-v)q-g_r\mu\\
    &=(\Pi(q,p^o)+g\mu)-g_r\mu
\end{align*}
and so $q^o$ is optimal for the retailer and the supplier. Coordination occurs becasue the retailer's pricing decision is not distorted, and the retailer's quantity decision is adjusted \textbf{contingent} that $p^o$ is chosen.

\subsection{Discussion}
There are surely many situations in which a retailer has some control over his pricing. However, \textbf{incentives to coordinate the retailer's quantity decision may distort the retailer's price decision}. This occurs with the \textbf{buyback}, \textbf{quantity-flexibility} and the \textbf{sales-rebate} contracts. Since the \textbf{quantity discount} leaves all revenue with the retailer, it does not create such a distortion, which is an asset when the retailer's pricing decision should not be distorted, i.e., when $g_s=0$. \textbf{Revenue sharing} does not distort the retailer's pricing decision when $g_r=g_s=0$. In those situations the set of revenue-sharing contracts to coordinate the quantity decision with a fixed price continue to coordinate the quantity decision with a variable price. However, when there are goodwill costs, then the coordinating revenue-sharing parameters generally depend on the retail price. The dependence is removed with only a single revenue-sharing contract; hence coordination is only achieved with a single profit allocation\footnote{$\phi=g_r/g$.}. Coordination is restored with arbitrary profit allocation by making the parameters contingent on the retail price chosen, e.g., a menu of revenue-sharing contracts is offered that depend on the price selected. This technique also applies to the buyback contract: the \textbf{price contingent buyback} contract, which is also called a price-discount-sharing contract, coordinates the price-setting newsvendor. In fact, just as buybacks and revenue sharing are equivalent with a fixed retail price, the \textbf{price contingent buybac} and \textbf{revenue sharing} are equivalent when there are no goodwill costs. When there are goodwill costs then the \textbf{price contingent buy back} is equivalent to the \textbf{price contingen revenue-sharing}  contract.

















